Jesse Lu

### 2013-07-26 resume/cv.tex
Updated cv with UCLA GPA.

\section{Education}          
    Stanford University, PhD, Electrical Engineering, June 2013 (GPA: 3.657)\\
    Stanford University, Masters of Science, Electrical Engineering, May 2012 \\
    University of California Los Angeles, Bachelor of Science, Electrical Engineering, June 2006

@@

\section{Programming}          
    Fluent in Python, CUDA, C, C++, and Matlab. \\
    Implemented cloud-based simulation service on Amazon EC2. \\
    Developed hardware-accelerated time- and frequency-domain
        electromagnetic solvers. \\
    Developed Matlab library for the design of arbitrary linear nanophotonic components.

>>>>

\section{Education}          
    Stanford University, Ph.D., Electrical Engineering, June 2013 (GPA: 3.657)\\
    Stanford University, M.S. , Electrical Engineering, May 2012 (GPA: 3.657)\\
    University of California Los Angeles, B.S., Electrical Engineering, June 2006 (GPA: 3.769)

@@

\section{Programming}          
    Fluent in Python, CUDA, Linux, C, C++, and Matlab. \\
    Implemented cloud-based simulation service on Amazon EC2. \\
    Developed hardware-accelerated time- and frequency-domain
        electromagnetic solvers. \\
    Developed Matlab library for the design of arbitrary linear nanophotonic components.
